---
title: "The Sequential CRT Examples"
output:
  html_document:
    df_print: paged
---

We demonstrate the usage of the functions here. 
```{r echo=T, results='hide'}
source("../sequential_CRT/sequential_CRT_functions.R")
```

### Generate Data
We start by generating a small dataset. 
```{r}
set.seed(2021)
n = 100 ## number of observations
p = 50 ## number of variables
k = 20 ## number of nonnulls
amplitude = 10
rho = 0.5

##generate X from a gaussian distribution and generate Y from a linear model
nonnulls = sample(1:p,k)
beta = rep(amplitude,k)/sqrt(n)
y_model = function(X){
    y = X %*% beta
}
Sigma = toeplitz(rho^(0:(p-1)))
X = matrix(rnorm(n*p),n) %*% chol(Sigma)
y = y_model(X[,nonnulls]) + rnorm(n) 
```

### Run the procedures
We run the the sequential CRT (split version and symmetric statistics version), and knockoffs as a comparison.
```{r echo=T, results='hide'}
selected_sets = selected_set(X, y, X_model = "AR", rho = 0.5, Sigma = Sigma, model = "linear", blackbox = "lasso", c = 0.1, include_h = FALSE, knockoff_pluss = 1)
```
We find the FDP and power of the procedures.
```{r}
##find fdps and powers
fdp = function(selected, nonnulls) length(setdiff(selected, nonnulls)) / max(1, length(selected))
power = function(selected, nonnulls) length(intersect(selected, nonnulls)) / length(nonnulls)
fdps = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, fdp))
powers = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, power))

results = data.frame(fdp = fdps, power= powers, method = selected_sets$method)
results
```

### Change the blackbox to compute importance statistics
One can also run the procedures with a different blackbox, e.g., gradient boosting.
```{r echo=T, results='hide'}
selected_sets = selected_set(X, y, X_model = "AR", rho = 0.5, Sigma = Sigma, model = "linear", blackbox = "gb", c = 0.1, include_h = FALSE, knockoff_pluss = 1)
```
Again, we find the FDP and power of the procedures.
```{r}
fdps = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, fdp))
powers = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, power))
results = data.frame(fdp = fdps, power= powers, method = selected_sets$method)
results
```

### Binary data

We generate a small dataset where $y$ is binary. 
```{r}
amplitude = 40
rho = 0.5

##generate X from a gaussian distribution and generate Y from a linear model
nonnulls = sample(1:p,k)
beta = rep(amplitude,k)/sqrt(n)
Sigma = toeplitz(rho^(0:(p-1)))
X = matrix(rnorm(n*p),n) %*% chol(Sigma)
y_model = function(X){
                y = X %*% beta
            }
z = y_model(X[,nonnulls])
pr = 1/(1+exp(-z))         # pass through an inv-logit function
y = (runif(n)<pr) + 0
```

Then we run our procedures and find FDP and power. 
```{r echo=T, results='hide'}
selected_sets = selected_set(X, y, X_model = "AR", rho = 0.5, Sigma = Sigma, model = "logistic", blackbox = "lasso", c = 0.1, include_h = FALSE, knockoff_pluss = 1)
```

```{r}
fdps = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, fdp))
powers = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, power))
results = data.frame(fdp = fdps, power= powers, method = selected_sets$method)
results
```


### HMM model
The code also works for the case where $X$ is sampled from an HMM
```{r}
amplitude = 50

## Define an HMM 
K=5  # Number of possible states for each variable
M=3  # Number of possible emission states for each variable
States = 1:K
Symbols = 1:M
startProbs = rep(1,K)/K
rho = 0.5
transProbs = (1-rho)*matrix(rep(1/K,(K^2)), ncol = K) + rho*diag(rep(1,K))
rho2 = 0.5
Diag_g = matrix(c(rep(c(1,0.5,rep(0,(K*M-1)/(M-1)-3),0.5),M-1), 1), ncol = M)
emissionProbs = (1-rho2)*matrix(rep(1/M,(K*M)), ncol = M) + rho2*Diag_g
hmm1 = initHMM(States, Symbols, startProbs, transProbs, emissionProbs)

##generate random samples
nonnulls = sample(1:p,k)
beta = rep(amplitude,k)/sqrt(n)
y_model = function(X){
    y = (X-2) %*% beta
}
Sigma = toeplitz(rho^(0:(p-1)))
X = matrix(rep(0,n*p), nrow = n)
for (i in 1:n){
    X[i,] = simHMM(hmm1, length = p)$observation
}
z = y_model(X[,nonnulls]) + rnorm(n) 
pr = 1/(1+exp(-z))         # pass through an inv-logit function
y = (runif(n)<pr) + 0
```

Again we run our procedures and find FDP and power. 
```{r echo=T, results='hide'}
selected_sets = selected_set(X, y, X_model = "HMM", hmm = hmm1, model = "logistic", blackbox = "lasso", c = 0.1, include_h = FALSE, knockoff_pluss = 1)
```

```{r}
fdps = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, fdp))
powers = unlist(lapply(selected_sets$selected_list, nonnulls = nonnulls, power))
results = data.frame(fdp = fdps, power= powers, method = selected_sets$method)
results
```
